### 2013-07-05 tests_test.Rmd
added monitorFunction

source("gapolyfuncs.R")
report <- make.report(my.data, population=50, iterations=25, mutation.rate=0.05)

@@

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=10, iterations=25)

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=50, iterations=25, mutation.rate=0.05, runs=1)

@@

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=10, iterations=10)
